The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-08-31 design.tex
modify

% !TEX root = Eco-Model.tex
\section{Design of the ecosystem} % (fold)
\label{sec:design_of_the_ecosystem}
\subsection{Preliminaries} % (fold)
\label{sub:preliminaries}
The manufacturing ecosystem we proposed in this paper consists of the structure of cloud manufacturing, the operation mode and the controlling rules. Before the detailed interpretation for these parts, we describe some basic settings as follows.

\begin{figure}[htbp]
    \centering
    \resizebox{0.9\textwidth}{!}{\input{figures/origin_mode}}
    \caption{Origin mode}
    \label{fig:originmode}
\end{figure}

\subsubsection{Assumptions} % (fold)
\label{ssub:assumptions_nomenclature}
Assumptions about quality

about time

schedule and outsource are event driven decision making

resources are renewable

\begin{table}[htbp]
  \scriptsize
\begin{tabularx}{\textwidth}{|lX|}
    \hline
    \multicolumn{2}{|l|}{\multirow{2}[0]{*}{\textbf{Nomencalture}}} \\
    \multicolumn{2}{|l|}{} \\
	$o_i$ & Order that come with demander \\
	$\mathcal{T}_i$ & Task set of $o_i$ \\
	$t_{ij}$ & Task belongs to $o_i$, $t_{ij}\in\mathcal{T}_i$ \\
	$p_{ij}$ & Process duration of $t_{ij}$\\
	$\gamma_{ij}$ & Expect quality of product after the finish of $t_{ij}$\\
	$r_i$ & Release time of $o_i$\\
	$f_{ij}$ & Actual finish time of $t_{ij}$ \\
	$f_{i}$ & Finish time of $o_i$\\
	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$\\
	$mr_k$ & Resource that come with provider \\
	$\delta_k$ & Product quality produced via resource $mr_k$ \\
	$C_{k,\tau}$ & Capacity of $mr_k$ at time $\tau$\\
	$A_{k,\tau}$ & Available capacity of $mr_k$ at time $\tau$\\
	$\mathcal{L}_{k,\tau}$ & The list of job queue of $mr_k$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $mr_k$ at $\tau$ \\ 
	$f^{(s)}_j$ & Ideal finish time of $t_j$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule . \\
	$re_j$ & Remaining process time of $t_j$ in $\mathcal{G}_{k,\tau_0}$ for schedule . \\
	$\mathcal{A}$ & Resource type set \\
	$\mathcal{A}_{ij}$ & Resource type subset required by $t_{ij}$, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
	$q_{\alpha,ij}$ & Required amount of resource with type $\alpha$ by $t_{ij}$\\
	$sc_l$ & Service-call generated by provider\\
	$p_l$ & Process duration of $sc_l$\\
	$r_l$ & Release time of $sc_l$\\
	$\mathcal{P}_{l}$ & The set of predecessor of $sc_{l}$\\
	$\mathcal{A}_l$ & Resource type subset required by $sc_l$ or provided by $ms_l$ , $\mathcal{A}_l\subset\mathcal{A}$\\
	$ms_l$ & Service that generated after the finish of $sc_l$\\
	$\Delta_l$ & Product quality produced via service $ms_l$\\
	$\bm{mr}_l$ & Resource member set of $ms_l$\\
	$\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\
	$\mathcal{L}_{l,\tau}$ & The list of job queue of $ms_l$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $ms_l$ at $\tau$ \\
	$\mathcal{R}_{ij,\tau}$ & Resource candidates set for $t_{ij}$ to select\\
	$\mathcal{B}_{ij,\tau}$ & Resource candidate types set for $t_{ij}$\\
	$\mathcal{S}_{ij,\tau}$ & Service candidates set for $t_{ij}$ to select\\
	$\mathcal{R}_{l,\tau}$ & Resource candidates set for $sc_l$ to select\\
	$\mathcal{B}_{l,\tau}$ & Resource candidate types set for $sc_l$\\
	$R(\cdot)$ & Rank inquire function about provider\\
	$F(\cdot)$ & Owner inquire function about resource or service\\
	$P(\cdot)$ & Type inquire function about resource type\\
	$\bm{x}$ & Bold font of the variable($x$) means the temp set of a bunch of these variables\\
    \hline
\end{tabularx}
\end{table}

For the continuous coming of provider, demander, order, task, etc., the amount of them can not be determined at any time point, so we doesn't restrict the upper bound for subscript index amount of all these variables, and we will study the decision separately for these individual at the given time point $\tau$. Detailed design will be explained in the following sections.
% subsubsection assumptions_nomenclature (end)
\subsubsection{Master plan} % (fold)
\label{ssub:master_plam}

A single order($o_i$) consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks which have to be processed. The tasks are interrelated by kinds of constraints. First, precedence constraints force task $t_{ij}$ not to be started before all its immediate predecessors, how to construct the predecessor will be explained later. Second, performing the tasks requires resources with limited capacities. Third, resources cooperation transmits and enhances these constraints.

A single resource($mr_k$) belongs to one type in set $\mathcal{A} = \left\{1,2,\dots\right\}$ given by the platform. While being processed via resource cooperation, task $t_{ij}$ requires $q_{k,ij}$ units amount of the resources with every type in $\mathcal{A}_{ij}\subset\mathcal{A}$ during every period of its non-preemptable duration $p_{ij}$. Each resource $mr_k$ has a limited capacity of $C_{k,\tau}$ at any point in time $\tau$.

@@

\subsection{Individual decisions and ecosystem mode options} % (fold)
\label{sub:interactions_and_decisions}

\subsubsection{Selection in resource candidates}
\label{subs:Demander}
Demander makes decision about resources and services selection for the task. Without loss of generalization, we suppose at time period $\tau$, demander received bunch of matched resource and services as candidates for the performance of the published order $o_i$, it's obvious that $\tau \ge r_{i}$. The decision making for any task included in $o_i$, let's take $t_{ij}$, can be described in one of the following 3 situation:

\begin{equation}
\max_{\forall l}\left( \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)
\end{equation}
\begin{numcases}{\text{s.t.}}
\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \\
l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & 
\end{numcases}

\subsubsection{Response in selected resource}
\label{subs:Provider}
Provider makes decision for job response with regard to its resources and service, the job here is the generalization of task and service-call. As we mentioned in the master plan, provider publish service-call according to the frequent accomplished tasks. Without loss of generalization, we suppose at time $\tau$, demander will make these decisions:

\begin{asparaenum}
\item Response for the task need $t_{ij}$($\tau\ge r_i$) with resource $mr_k$
\suspend{asparaenum}
\begin{subnumcases}{}
A_{k,\tau} \ge q_{\alpha,ij} &\\
P(mr_k) = \alpha & 
\end{subnumcases}
If $mr_k$ meets the above condition, provider of it will response the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$. If $mr_k$ was finally chose, available of $mr_k$ will change as $A_{k,\tau}:= A_{k,\tau} - q_{\alpha,ij}$. The available will be return back after the finish of $t_{ij}$.
\resume{asparaenum}
\item Response for the service-call need $sc_l$($\tau\ge r_l$) with resume $mr_k$
\suspend{asparaenum}
\begin{subnumcases}{}
C_{k,\tau} > 0 & \\
P(mr_k) = \alpha
\end{subnumcases}
If $mr_k$ meets the above condition, provider($p_a$) of it will response the service-call need, the provider($p_b$) of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$, it's possible to let $p_a=p_b$. If $mr_k$ was finally chose, capacity of $mr_k$ will change as:
\begin{subnumcases}{}
C_{k,\tau} := C_{k,\tau} - q_{\alpha,l}& If $C_{k,\tau} \ge q_{\alpha,l}$\\
C_{k,\tau} := 0 & otherwise
\end{subnumcases}

Capacity will not return back to $mr_k$ until the corresponding service $ms_l$ was repealed. Decision making of provider $p_b$ likes the one of demander's, but the final decision $\bm{mr}_l$ and $\bm{q}_l$ don't have to meet $\abs{\bm{mr}_l} = \abs{\mathcal{A}_{ij}}$, because different resource with the same type can gather together to bundle into one service, the only condition in need is that
\begin{subnumcases}{}
\sum_{k\in\mathcal{R}_{\alpha,\tau}} q_{\alpha,k} = q_{\alpha,l} & $\forall\alpha\in\mathcal{A}_l$\\
R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{l,\tau}, P(mr) = \alpha \right\} & $\forall\alpha\in\mathcal{A}_l$
\end{subnumcases}
\resume{asparaenum}
\item Response for the task need $t_{ij}$($\tau\ge r_i$) with service $ms_l$.
\end{asparaenum}
Service is a combination contract among the participated resources and it's made oriented to the certain task, so the only condition for $ms_l$ to response $t_{ij}$ is:
\begin{subnumcases}{}
q_{\alpha,ij} = q_{\alpha,l} & $\forall\alpha\in\mathcal{B}_l$\\
\mathcal{A}_{ij} = \mathcal{B}_l
\end{subnumcases}

This condition is much same as service-call need $sc_l$ after the accomplishment frequent task $t_{ij}$:
\begin{subnumcases}{}
q_{\alpha,ij} = q_{\alpha,l} & $\forall\alpha\in\mathcal{A}_l$\\
\mathcal{A}_{ij} = \mathcal{A}_l
\end{subnumcases}
% subsection interactions_and_decisions (end)

\subsection{Incubation mode} % (fold)
\label{sub:incubation_mode}
The chief decision making about operation mode for provider is the job schedule method outsource mode, as we mentioned in the master plan, provider makes these decision to arrange the job for a better performance in the process procedure. Because of the event driven assumptions, we again suppose that both a new task was assigned to service or resource and a job was finished at time $\tau$, provider will make decision in the following conditions:

A single service($s_l$) is a composition of all resources in set $\bm{mr}_l$ with their partial capacities, it can only process certain task with matched resource configuration($\mathcal{A}_{ij}=\mathcal{A}_l$,$ Q_{ij}(\cdot)=Q_l(\cdot)$) without resource coordinating any more. While being processed via one matched service, task can be suspended then outsourced to other matched service or resource cooperation.
Resource comes along with provider when it enter the ecosystem, however, service doesn't, service is generated after a period of time, the prototype of a service is another type of job, we call it the service-call.

A single service-call($sc_l$) comes out after the finish of one frequent task, so it have the same resource configuration the frequent task. Service-call can only be performed via resource cooperation with duration $p_l$, because the identity of resource, the capacity cannot be return to the resource after the finish of service-call, so the service-call brings new constrains to the related resources. Unlike the task, the amount of one type resource required in the service-call can be pieced together from more than one resource as long as they are in the same type.

\begin{figure}[htbp]
    \centering
    \resizebox{0.7\textwidth}{!}{\input{figures/service-incubate}}
    \caption{Service incubate mode}
    \label{fig:serviceincubatemode}
\end{figure}

\begin{asparaenum}
\item $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij}$, while $|\mathcal{S}_{ij,\tau}|>0$.
\suspend{asparaenum}

\resume{asparaenum}
\item  $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$, while $\abs{\mathcal{S}_{ij,\tau}}=0$.
\suspend{asparaenum}

\begin{equation}
\max_{\forall \bm{k}}\left( \delta_{\bm{k}}, 
R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
\right)
\end{equation}

\begin{numcases}{\text{s.t.}}
q_{\alpha,ij} \le C_{k_{\alpha},\tau} & $\alpha\in\mathcal{A}_{ij}$\\
R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & $\alpha\in\mathcal{A}_{ij}$\\
\mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
\bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right] & \\
k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &$\alpha\in\mathcal{A}_{ij}$
\end{numcases}
For each required resource type $\alpha$

\resume{asparaenum}
\item  $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$, while $\abs{\mathcal{S}_{ij,\tau}}>0$.
\end{asparaenum}

\begin{equation}
\max_{m\in\{l^*,\bm{k}^*\}} \left( \Delta_m, 
Rank_m, \mathcal{L}_m \right) \\ 
% \text{s.t.}\notag
\end{equation}
\begin{numcases}{\text{s.t.}}
% q_{\alpha,ij} \le C_{k_{\alpha},\tau} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
% R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
% \mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
% \bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right]& \\
% k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &\footnotesize$\alpha\in\mathcal{A}_{ij}$ \\
\bm{k}^* = \arg\left(\max_{\forall \bm{k}}\left( \delta_{\bm{k}}, 
R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
\right)\right) & \\
Rank_{\bm{k}^*} = \min_{k\in\bm{k}^*} \left\{ R\left( F\left( mr_k \right) \right) \right\} & \\
\mathcal{L}_{\bm{k}^*} = \max_{k\in\bm{k}^*}\left\{ \abs{\mathcal{L}_{k,\tau}} \right\} & \\
\Delta_{\bm{k}^*} \sim \mathcal{N} \left(\mu_{\bm{k}^*},\sigma_{\bm{k}^*}^2\right) & \\
\mu_{\bm{k}^*} = mean\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
\sigma_{\bm{k}^*} = std\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
\bm{mr}_{\bm{k}^*} = \bigcup_{k\in\bm{k}^*}mr_k  &\\
\bm{q}_{\bm{k}^*}  =\bigcup_{\alpha\in\mathcal{A}_{ij}}q_{\alpha,ij} & \\
% \Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
% \mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
% \sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \\
% l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \\
l^* = \arg\left( \max_{\forall l}\left(\Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)  \right) & \\
Rank_{l^*} = R\left( F\left( ms_{l^*} \right) \right) & \\
\mathcal{L}_{l^*} = \abs{\mathcal{L}_{l^*,\tau}} & \\
m \in \left\{ l^*,\bm{k}^* \right\} 
\end{numcases}

\begin{asparaenum}
\item Assign new task $t_{ij}$ in $mr_k$.
\suspend{asparaenum}

>>>>

% !TEX root = Eco-Model.tex
\section{Design of the ecosystem} % (fold)
\label{sec:design_of_the_ecosystem}
\subsection{Preliminaries} % (fold)
\label{sub:preliminaries}
With the cloud manufacturing platform operating, demander publish orders while provider provide resources, then they communicate with each other, arrange the resources to perform tasks that decomposed by orders. Finally, product is produced and delivered to the demander. Most recent researchers like Wu et al.\cite{Wu2013} describe this operation procedure in cloud manufacturing as a tri-group user model that contains:\begin{inparaenum}[1)]
\item Users/Customers,
\item Application providers and
\item Physical resource providers.
\end{inparaenum}
Inspired by the such model, we design the original mode shown in \autoref{fig:originmode} as the basis for the operating of the platform.
\begin{figure}[htbp]
    \centering
    \resizebox{0.9\textwidth}{!}{\input{figures/origin_mode}}
    \caption{Original mode}
    \label{fig:originmode}
\end{figure}
In this mode, individual in each group execute activities that interact with others with object flow(full lines) and information flow(dashed lines). As the start of manufacturing activities procedure, the demander publish orders that can be depicted by a so-called activity-on-node(AON) network where the nodes represent the tasks and the arcs the precedence relations. Each task needs to performed with pre-determined configuration of resources, hence, after the response and assign procedure, the selected resource cannot start to process the task until all of other selected resources by this task are ready, we call this procedure as resource cooperating and what each resource actually process is the task part. Finally product will be delivered to demander after the process and assembly of these parts, then the review of the product will change the rank value of the selected resource owners. Task part is a virtual segmentation of one task, it just like if we run one program in cloud computing platform, we actually use some quota of provider A's DB and some quota of provider B's CPU, we can consider them as task parts. A little more about the cooperation procedure, this produce is necessary because the capacity limit of resources and task part should be processed simultaneously to make sure that the task is being processed with required resource capacities. We call the task part is active when being processed, semi-active when resource is waiting for synchronization, inactive when the part is just assigned to the job list.

\subsubsection{Assumptions} % (fold)
\label{ssub:assumptions_nomenclature}
To scope our research, we make some assumptions as follows:
\begin{compactitem}
\item Each single task should be assembled by part according to the pre-determined resources configuration, and these parts should be processed simultaneously;
\item Since the cooperation, the quality of product is determined by the worst quality part of produced by selected resource;
\item Resource are renewable that the available capacity will be return when the process produce finished;
\item Resource quality comply normal distribution with given mean and standard deviation by provider when registered;
\item Cooperate and process produce cannot be interrupted;
\item Provider can only schedule task part that in inactive status. 
\end{compactitem}
These assumptions are suitable for original mode, in other extension mode, some of the assumptions will be modified.

\begin{table}[htbp]
  \scriptsize
\begin{tabularx}{\textwidth}{|lX|}
    \hline
    \multicolumn{2}{|l|}{\multirow{2}[0]{*}{\textbf{Nomencalture}}} \\
    \multicolumn{2}{|l|}{} \\
	$o_i$ & Order that come with demander \\
	$\mathcal{T}_i$ & Task set of $o_i$ \\
	$t_{ij}$ & Task belongs to $o_i$, $t_{ij}\in\mathcal{T}_i$ \\
	$p_{ij}$ & Process duration of $t_{ij}$\\
	$\gamma_{ij}$ & Expect quality of product after the finish of $t_{ij}$\\
	$r_i$ & Release time of $o_i$\\
	$f_{ij}$ & Actual finish time of $t_{ij}$ \\
	$f_{i}$ & Finish time of $o_i$\\
	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$\\
	$mr_k$ & Resource that come with provider \\
	$\delta_k$ & Product quality produced via resource $mr_k$ \\
	$C_{k,\tau}$ & Capacity of $mr_k$ at time $\tau$\\
	$A_{k,\tau}$ & Available capacity of $mr_k$ at time $\tau$\\
	$\mathcal{L}_{k,\tau}$ & The list of inactive job queue of $mr_k$ at $\tau$ with sequence\\
	$\mathcal{H}_{k,\tau}$ & The list of semi-active job of $mr_k$ at $\tau$ \\
	$\mathcal{G}_{k,\tau}$ & The set of active job of $mr_k$ at $\tau$ \\ 
	$f^{(s)}_j$ & Ideal finish time of $t_j$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule . \\
	$re_j$ & Remaining process time of $t_j$ in $\mathcal{G}_{k,\tau_0}$ for schedule . \\
	$\mathcal{A}$ & Resource type set \\
	$\mathcal{A}_{ij}$ & Resource type subset required by $t_{ij}$, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
	$q_{\alpha,ij}$ & Required amount of resource with type $\alpha$ by $t_{ij}$\\
	$sc_l$ & Service-call generated by provider\\
	$p_l$ & Process duration of $sc_l$\\
	$r_l$ & Release time of $sc_l$\\
	$\mathcal{P}_{l}$ & The set of predecessor of $sc_{l}$\\
	$\mathcal{A}_l$ & Resource type subset required by $sc_l$ or provided by $ms_l$ , $\mathcal{A}_l\subset\mathcal{A}$\\
	$ms_l$ & Service that generated after the finish of $sc_l$\\
	$\Delta_l$ & Product quality produced via service $ms_l$\\
	$\bm{mr}_l$ & Resource member set of $ms_l$\\
	$\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\
	$q_{\alpha,l}$ & Need resource capacity of $sc_l$ with type $\alpha$\\
	$\bm{\alpha}_l$ & Subset of $\bm{q}_l$ that consists of all the capacities of type $\alpha$ resources in $\bm{mr}_l$\\
	$\mathcal{L}_{l,\tau}$ & The list of job queue of $ms_l$ at $\tau$ with sequence\\
	$\mathcal{G}_{l,\tau}$ & The set of active job of $ms_l$ at $\tau$ \\
	$\mathcal{R}_{ij,\tau}$ & Resource candidates set for $t_{ij}$ to select\\
	$\mathcal{B}_{ij,\tau}$ & Resource candidate types set for $t_{ij}$\\
	$\mathcal{S}_{ij,\tau}$ & Service candidates set for $t_{ij}$ to select\\
	$\mathcal{R}_{l,\tau}$ & Resource candidates set for $sc_l$ to select\\
	$\mathcal{B}_{l,\tau}$ & Resource candidate types set for $sc_l$\\
	$R(\cdot)$ & Rank inquire function about provider\\
	$F(\cdot)$ & Owner inquire function about resource or service\\
	$P(\cdot)$ & Type inquire function about resource type\\
	$\bm{x}$ & Bold font of the variable($x$) means the temp set of a bunch of these variables\\
    \hline
\end{tabularx}
\end{table}
\vspace{-2.5em}
% subsubsection assumptions_nomenclature (end)
\subsubsection{Master plan for original mode} % (fold)
\label{ssub:master_plam}
A single order($o_i$) consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, the tasks are interrelated by kinds of constraints. First, precedence constraints force task $t_{ij}$ not to be started before all its immediate predecessors that come along within order and it can be added in the schedule produce. Second, performing the tasks requires resources with limited capacities. Third, resources cooperation requires all the task parts in active status.
A single resource($mr_k$) belongs to one type in set $\mathcal{A} = \left\{1,2,\dots\right\}$ given by the platform. While being processed via resource cooperation, task $t_{ij}$ requires $q_{\alpha,ij}$ units capacity of the resources with each type $\alpha\in\mathcal{A}_{ij}\subset\mathcal{A}$ during every period of its non-preemptable duration $p_{ij}$. Each resource $mr_k$ has a limited capacity of $C_{k,\tau}$ at any point in time $\tau$. This plan is much like the settings in resource-constrained project scheduling problem\cite{Kolisch1999} except that the task here need multiple types of resource simultaneously.

@@

\subsection{Individual decisions in original mode} % (fold)
\label{sub:interactions_and_decisions}
\subsubsection{Response for type matched task}
\label{subs:Response_for_type_matched_task}
Provider makes decision at time $\tau\ge r_i$ to response task if the belonged resource $mr_k$ was type matched with $t_{ij}$ ($P(mr_k)\in\mathcal{A}_{ij}$). If $A_{k,\tau} \ge q_{\alpha,ij}$, provider will response the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{ij,\tau}$. If $mr_k$ was finally selected, available capacity of $mr_k$ will change as $A_{k,\tau}:= A_{k,\tau} - q_{\alpha,ij}$ , the available capacity will be returned back after the finish of $t_{ij}$ part.

\subsubsection{Select from resource candidates}
\label{subs:select_resource_candidates}
Demander makes decision about resource selection from $\mathcal{R}_{ij,\tau}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$. W.o.l.o.g, we suppose at time period $\tau \ge r_i$, the decision making of demander can be described as follows:
\begin{equation}
\max_{\forall \bm{k}}\left( \delta_{\bm{k}}, 
R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
\right) \label{eq:selectresaim}
\end{equation}
\begin{numcases}{\text{s.t.}}
q_{\alpha,ij} \le C_{k_{\alpha},\tau} & $\alpha\in\mathcal{A}_{ij}$\label{eq:rescaplimit}\\
\mathcal{R}_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & $\alpha\in\mathcal{A}_{ij}$\label{eq:restypeabstract}\\
\mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \label{eq:nrc}\\
\bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right] & \label{eq:decisionvectork}\\
k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &$\alpha\in\mathcal{A}_{ij}$ \label{eq:decisionvark}
\end{numcases}

The multi-objective in \autoref{eq:selectresaim} aims at high quality, high resource owner rank and low waiting queue length. \autoref{eq:rescaplimit} makes sure that resource capacity is capable to process the task part, \autoref{eq:restypeabstract}--\ref{eq:nrc} restrict the resource candidates' type in the task configuration, \autoref{eq:decisionvectork}--\ref{eq:decisionvark} describe decision variable, the demander should make decision to select resource in each type of required configuration.

\subsubsection{Assign in selected resource} % (fold)
\label{subs:assign_in_select_resource}
If $mr_k$ was selected by the demander of $t_{ij}$, then the provider will add $t_{ij}$ part to $\mathcal{H}_{k,\tau}$ or $\mathcal{L}_{k,\tau}$ according to:
\begin{subnumcases}{}
\mathcal{H}_{k,\tau} := \mathcal{H}_{k,\tau} \cup \{t_{ij}\} & if $\abs{\mathcal{L}_{k,\tau}}=0,A_{k,\tau}\ge q_{\alpha,ij}$ \label{eq:addtobuffer}\\
\mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
\end{subnumcases}

If all the part of $t_{ij}$ are in type matched resources' $\mathcal{H}_{k,\tau}$, then these providers will change all the task part status from semi-active to active and add $t_{ij}$ to their $\mathcal{G}_{k,\tau}$.
% subsubsection assign_in_selected_resource (end)
% subsection interactions_and_decisions (end)

\subsection{Incubation mode} % (fold)
\label{sub:incubation_mode}
Incubation mode is one extension mode for the original mode, the purpose of this mode is to remove the cooperation and assembly procedure in advance by gathering types of resource with certain quota in a contract. Manufacturing service will be incubated as shown in \autoref{fig:serviceincubatemode}.  
\begin{figure}[htbp]
    \centering
    \resizebox{0.7\textwidth}{!}{\input{figures/service-incubate}}
    \caption{Incubation mode}
    \label{fig:serviceincubatemode}
\end{figure}
After the finish of task part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such task-specified service for the future performance.

The first thing of incubation is to publish a job named service-call, which is similar with task except for the capacity dominance and each required resource type can also be cooperated by different resources, which means after the performance of service-call, capacity of selected resource will not be returned to. The product of service-call is the service, which is actually a contract of resources that may come from any provider in the system, it's possible for more than one resource with same type to make contribute to the formation of service. No more cooperation and assembly are part of pros of service and product quality will no more restricted to the worst quality of resources since the complementary effect, while the cons of service include that it can only perform  corresponding configured task.
Now we can mark task and service-call as job, resource and service as machine.

\subsubsection{Response for type matched job} % (fold)
\label{ssub:response_in_type_matched_resource}
Apart from $mr_k$ response for $t_{ij}$ as we explained in \autoref{subs:Response_for_type_matched_task}, there are 2 other cases in incubation mode:
\begin{asparaenum}
\item $mr_k$ response for $sc_l$
\suspend{asparaenum}
If $mr_k$ was type matched with $sc_l$ ($P(mr_k)\in\mathcal{A}_l$), as long as $C_{k,\tau}> 0$, provider of $mr_k$ will response the service-call. If $mr_k$ was finally selected, both available capacity and capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and these capacity will not be returned back even after the finish of $sc_l$ part. Provider of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{l,\tau}$.
\resume{asparaenum}
\item $ms_l$ response for $t_{ij}$
\end{asparaenum}
Service is task-oriented machine, so if type matched ($\mathcal{A}_{ij} =\mathcal{A}_l,\sum_{q\in\bm{\alpha}_l} q = q_{\alpha,ij}$), provider of it will response $t_{ij}$ as soon as possible, demander will add $ms_l$ to $\mathcal{S}_{ij,\tau}$.

% subsubsection response_in_type_matched_resource (end)

\subsubsection{Select from machine candidates} % (fold)
\label{ssub:selection_in_resource_candidates_for_service_call}
Apart from demander of $t_{ij}$ select $mr_k$ as we explained in \autoref{subs:select_resource_candidates} when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}=0$, there are 3 other cases in incubation mode:

\begin{asparaenum}
\item Select $mr_k$ for $sc_l$ when $\mathcal{B}_{l,\tau} = \mathcal{A}_l$
\suspend{asparaenum}

The decision making of select from $\mathcal{R}_{l,\tau}$ is similar to \autoref{eq:selectresaim}--\ref{eq:decisionvark}, and the difference is that the every part of $\bm{l}_{\alpha}$ in decision variable $\bm{l}$ here is also a set of selected resources followed by \autoref{eq:capq}--\ref{eq:cap0}, and if the sum of capacity quantity in $\bm{l}_{\alpha}$ less than the $sc_l$ required, this selection will not to be executed.
\begin{subnumcases}{}
C_{k,\tau} := C_{k,\tau} - q_{\alpha,l}& If $C_{k,\tau} \ge q_{\alpha,l}$\label{eq:capq}\\
C_{k,\tau} := 0 & otherwise \label{eq:cap0}
\end{subnumcases}

\resume{asparaenum}
\item Select $ms_l$ for $t_{ij}$ when $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij},|\mathcal{S}_{ij,\tau}|>0$
\suspend{asparaenum}

This situation implies that the resource candidates are not enough while there exists service candidates, demander can just select service. 
\begin{equation}
\max_{\forall l}\left( \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)\label{eq:selectserviceaim}
\end{equation}
\begin{numcases}{\text{s.t.}}
\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \label{eq:servicecomplydist}\\
\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \label{eq:servicecomplydistend}\\
l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \label{eq:decisionvariablel}
\end{numcases}

Similar to \autoref{eq:selectresaim}, \autoref{eq:selectserviceaim} is also a multi-objective function that aims at high quality, high service owner rank and low waiting queue length. \autoref{eq:servicecomplydist}--\ref{eq:servicecomplydistend} explain the service quality distribution parameters, \autoref{eq:decisionvariablel} is the decision variable to select one service in $\mathcal{S}_{ij,\tau}$.

\resume{asparaenum}
\item Select machine for $t_{ij}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}>0$.
\end{asparaenum}
